---
title: "Unremarkable Reflections"
subtitle: "The Bland Apologia of Rockefeller's *Random Reminiscences of Men and Events*"
output: 
  word_document:
    reference_docx: "asp2_style_reference.docx"
---


```{R setup, echo = FALSE, cache = FALSE}
knitr::opts_knit$set(eval.after = 'fig.cap')
knitr::opts_chunk$set(echo = FALSE)
knitr::read_chunk('asp2_analysis.R')
```


```{r analysis}
<<load_analysis_packages>>
<<load_stopwords>>
<<read_and_preprocess_text>>
<<extract_chapters>>
<<extract_sections>>
<<extract_paragraphs>>
<<extract_sentences>>
<<extract_tokens>>
<<count_tokens>>
<<extract_hapax>>
<<type_token_ratio>>
```

```{r graphics}
<<load_graphics_packages>>
<<declare_fonts>>
<<load_and_check_system_fonts>>
<<load_and_check_windows_fonts>>
<<declare_colors>>
<<declare_desaturation_function>>
<<create_zipf_plot>>
<<create_ttr_plot>>
<<create_freq_plot>>
<<bind_plots>>
<<correlation>>
```


That a man of John D. Rockefeller's achievements should write memoirs is
unremarkable. The tone of the memoirs themselves, however, stands in stark 
contrast to the extraordinary contours of Rockefeller's life. It is colorless,
anodyne---almost affable---in its treatment of his past.

Rockefeller takes great pains to defend himself against accusations of
questionable business practices: In fact, his strident support for honesty
and fair dealing---and his later concern for philanthropy---stand out in
the text. His belt-and-braces approach to his own defense does seem more at
home in a modern media campaign than a 19^th^ century autobiography, though:
Perhaps his accusers are mistaken? Or jealous? Perhaps some underling acted
without his knowledge? Perhaps the harm done was not so great after all? One
wonders if the first luxury Rockefeller might have afforded was an affected
ignorance of the grittier aspects of his own business empire. One might also
speculate that his obsession with honesty---and defensiveness about the
means used to accumulate his wealth---stems from the reputation of his father, 
he being the only individual in these memoirs for whom Rockefeller has
anything but kind words.

Frequency analysis easily reveals the basic subject matter of Rockefeller's
work: "Business," "great," "oil," "money," and "men," with his own
"Standard Oil Company" being the most frequent trigram.[^1] Unfortunately this
is not enormously enlightening. A cursory examination of Rockefeller's life
might lead anyone to the same conclusion. Analysis of the Type-Token Ratio
is equally frustrating, as the majority of its variation is explained merely
by the length of the text.[^2] A simple reading of Rockefeller's work appears
more revealing than quantitative analysis.


```{r plot, fig.width=10, fig.height=5, dpi=600, fig.cap=caption}
caption <- str_c('Word frequencies are calculated after SMART stopword ',
                 'removal. The distribution of unfiltered words by contrast ',
                 'closely follows Zipf\'s Law.')
plots
```

[^1]: Word frequencies are calculated after removal of SMART stopwords
[^2]: Chapter length explains `r ttr_length_corr` of the variation in
      Type-Token Ratio
